### 2022-05-24 main/chapter_2ljets.tex
clarify why no jet met triggers

In short, all triggers require $\pt^{\ell_i}$ values to exceed thresholds in
the range $8\textrm{--}26~\eV[G]$.
To detail all trigger requirements and their variations with data period
would be too tedious and not enlightening, but their $\pt^{\ell_i}$ requirements
are summarized here.
\begin{itemize}
\item Electron pair: requirements vary between
\begin{itemize}
\item $\pt^{e_2} > 12~\eV[G]$ and
\item $\pt^{e_2} > 17~\eV[G]$.
\end{itemize}
\item Muon pair: various requirements include
\begin{itemize}
\item $\pt^{\mu_2} > 10~\eV[G]$,
\item $\pt^{\mu_2} > 14~\eV[G]$,
\item $\pt^{\mu_1} > 18~\eV[G]~\&~\pt^{\mu_2} > 8~\eV[G]$, and
\item $\pt^{\mu_1} > 22~\eV[G]~\&~\pt^{\mu_2} > 8~\eV[G]$.
\end{itemize}
\item Emu pair: various asymmetric requirements include
\begin{itemize}
\item $\pt^{e_1} > 17~\eV[G]~\&~\pt^{\mu_1} > 14~\eV[G]$,
\item $\pt^{e_1} > 7~\eV[G]~\&~\pt^{\mu_1} > 24~\eV[G]$, and
\item $\pt^{e_1} > 26~\eV[G]~\&~\pt^{\mu_1} > 8~\eV[G]$.
\end{itemize}
\end{itemize}
Trigger requirements have increased in hardness with time.

@@

Although jet and $\met$ triggers were not studied in detail, they require
hard objects: examples are approximately $\ptjone > 400~\eV[G]$,
$p_\mathrm{T}^{\,j_3} > 200~\eV[G]$, or
$\met > 100~\eV[G]$~\cite{atlas_twiki_lowest_unprescaled}.
Leptons are striking signals which \atlas\ can trigger on with much softer
requirements; lepton triggers allow us to use softer jets and $\met$,
which are relied upon throughout the $\twoljets$ analyses.

>>>>

In short, all triggers require $\pt^{\ell_i}$ values to exceed thresholds in
the range $8\textrm{--}26~\eV[G]$.
To detail all trigger requirements and their variations with data period
would be too tedious and not enlightening, but their $\pt^{\ell_i}$ requirements
are summarized here.
\begin{itemize}
\item Electron pair: requirements vary between
\begin{itemize}
\item $\pt^{e_2} > 12~\eV[G]$ and
\item $\pt^{e_2} > 17~\eV[G]$.
\end{itemize}
\item Muon pair: various requirements include
\begin{itemize}
\item $\pt^{\mu_2} > 10~\eV[G]$,
\item $\pt^{\mu_2} > 14~\eV[G]$,
\item $\pt^{\mu_1} > 18~\eV[G]~\&~\pt^{\mu_2} > 8~\eV[G]$, and
\item $\pt^{\mu_1} > 22~\eV[G]~\&~\pt^{\mu_2} > 8~\eV[G]$.
\end{itemize}
\item Emu pair: various asymmetric requirements include
\begin{itemize}
\item $\pt^{e_1} > 17~\eV[G]~\&~\pt^{\mu_1} > 14~\eV[G]$,
\item $\pt^{e_1} > 7~\eV[G]~\&~\pt^{\mu_1} > 24~\eV[G]$, and
\item $\pt^{e_1} > 26~\eV[G]~\&~\pt^{\mu_1} > 8~\eV[G]$.
\end{itemize}
\end{itemize}
Trigger requirements increase in hardness with time.

@@

Although jet and $\met$ triggers were not studied in detail, they require
hard objects: examples are approximately $\ptjone > 400~\eV[G]$,
$p_\mathrm{T}^{\,j_3} > 200~\eV[G]$, or
$\met > 100~\eV[G]$~\cite{atlas_twiki_lowest_unprescaled}.
Leptons, however, are striking signals which are produced as smaller background
rates, as they suppressed by electroweak couplings.
Therefore, \atlas\ can trigger on leptons with much softer requirements;
lepton triggers allow us to use softer jets and $\met$, which are relied upon
throughout the $\twoljets$ analyses.
